### 2023-12-11 main.tex
bib

The model studied in this paper is the {\em  multispecies stirring process with open boundaries}, i.e. the multispecies analogue of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}. 
This particle system is defined on a generic connected and undirected graph. At each site 
the maximal number of allowed particles {\color{blue}(also called \textit{maximal occupancy})} is $\nu\in \mathbb{N}$. These particles can be of $N-1$ types (or species). Two sites do interact when there is an edge between them and this interaction consists in swapping the occupations of these two sites (for a precise definition of the process see Section \ref{sec1}). 
Furthermore, reservoirs are attached at each site of the graph, creating and removing particle. The process becomes integrable when the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and the maximal number of allowed particles is fixed to be $\nu=1$,  see \cite{vanicat2017exact}. {\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and on the maximal number of particle hosted at each site}.
%{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
%We refer to the model as the {\em  multispecies stirring process with open boundaries}.
%

@@

\begin{remark} 
Without using duality but only  the definition $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and that
\begin{equation}
 \langle \tau |S_1=\begin{cases}
                    \sum_{\sigma=1}^N\langle \sigma|  \quad\text{if}\quad \tau=N\\
                    \langle \tau| \quad\text{else} 
                   \end{cases}\,,
\end{equation} 
  we immediately verify 
\begin{equation}\label{eq:EE}
\begin{split}
\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=
\langle N,\ldots,N,\underbrace{a_1}_{x_{1}},N,\ldots,N,\underbrace{a_m}_{x_{m}},N,\ldots,N|\Psi^{'}\rangle\dt
 \end{split}
\end{equation} 
{\color{blue}Here the notation means that the entries $a_k\neq N$ in \eqref{eq:EE} are at position $x_k$ for $k\in\{1,\ldots,m\}$.} 
\end{remark}

\todo{ok? adopt notation?}

@@

			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underbrace{a_{1}}_{q_{1}},\ldots,\underbrace{a_{b}}_{q_{b}},\ldots,\tau_{L})

>>>>

The model studied in this paper is the {\em  multispecies stirring process with open boundaries}, i.e. the multispecies analogue of the exclusion process on a generic graph as introduced in \cite{zhou2021orthogonal} with additional boundary reservoirs as proposed in \cite{vanicat2017exact}. 
This particle system is defined on a generic connected and undirected graph. At each site 
the maximal number of allowed particles {\color{blue}(also called \textit{maximal occupancy})} is $\nu\in \mathbb{N}$. These particles can be of $N-1$ types (or species). Two sites do interact when there is an edge between them and this interaction consists in swapping the occupations of these two sites (for a precise definition of the process see Section \ref{sec1}). 
Furthermore, reservoirs are attached at each site of the graph, creating and removing particle. The process becomes integrable when the graph is a finite chain with two reservoirs attached to the first and the last sites respectively and the maximal number of allowed particles is fixed to be $\nu=1$,  see \cite{vanicat2017exact}. {\color{blue}The choice of the boundary reservoirs introduced in \cite{vanicat2017exact} is further motivated by the fact that they allow to determine an absorbing dual process, regardless of the geometry on which the process is defined and regardless of the maximal number of particle hosted at each site ($\nu$ can any natural number)}.\\
{\color{blue}In this paper we concentrate our effort in studying the symmetric multispecies model. In literature, also multispecies asymmetric models have been introduced \cite{schutz2017kardar,crampe2016integrable, finn2018matrix} and integrability results have been proved. Moreover, different transition mechanism (beyond the diffusive one) have been recently studied \cite{chatterjee2023multi}. Finally, the presence of different types of particles have also been modelled via a "multi-layer" dynamics (see \cite{redig2022ergodic,floreani2022switching}). As far as we know, in these contexts integrability does not hold.} 
%{\color{red}Explain the model here.... $N$-species (or $N-1$ plus empty?). What is the graph? say that it becomes integrable for the line }
%We refer to the model as the {\em  multispecies stirring process with open boundaries}.
%

@@

\begin{remark} 
Without using duality but only  the definition $|\Psi^{'}\rangle=S_1|\Psi\rangle$ and that
\begin{equation}
 \langle \tau |S_1=\begin{cases}
                    \sum_{\sigma=1}^N\langle \sigma|  \quad\text{if}\quad \tau=N\\
                    \langle \tau| \quad\text{else} 
                   \end{cases}\,,
\end{equation} 
  we immediately verify 
\begin{equation}\label{eq:EE}
\begin{split}
\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in\Omega^{'}}\prod_{k=1}^{m}\delta_{{{\tau}_{x_k}},a_{k}}\langle \bm{\tau}|\Psi\rangle=
\langle N,\ldots,N,\underset{\uparrow}{a_1}_{x_{1}},N,\ldots,N,\underset{\uparrow}{a_m}_{x_{m}},N,\ldots,N|\Psi^{'}\rangle\dt
 \end{split}
\end{equation} 
{\color{blue}Here the notation means that the entries $a_k\neq N$ in \eqref{eq:EE} are at position $x_k$ for $k\in\{1,\ldots,m\}$.} 
\end{remark}

\todo{ok? adopt notation?[DONE]}

@@

			=&\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}^{L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{1},\ldots a_{b}=1}^{N-1}\Psi^{'}(\tau_{1},\ldots,\underset{\uparrow}{a_{1}}_{q_{1}},\ldots,\underset{\uparrow}{a_{b}}_{q_{b}},\ldots,\tau_{L})
